Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-19 optim.qmd

```{r fig-idx-proj-dist}
#| fig.width = 9,
#| fig.height = 5,
#| fig.cap = "Index values versus projection distance for the 12 pipe/sine-wave finding problem, after the binning procedure for calculating the squintability measure. The index values, averaged at bin width of 0.005, are scaled from 0 to 1 for comparison (holes, TIC, and stringy). The `MIC` and `TIC` index curves are convex while others are concave. The stringy curve shows an instantaneous jump to the optimum when aproaching the best basis." 
sq_basis_dist_idx |>
  ggplot(aes(x = dist, y = idx, group = index)) +
  geom_line() +
  facet_nested_wrap(~index + n, nrow = 3, labeller = label_both) + 
  xlab("projection distance") + ylab("index value")

>>>>

```{r fig-idx-proj-dist}
#| fig.width = 9,
#| fig.height = 5,
#| fig.cap = "Index values versus projection distance for the 12 pipe/sine-wave finding problem, after the binning procedure for calculating the squintability measure. The index values, averaged at bin width of 0.005, are scaled from 0 to 1 for comparison (holes, TIC, and stringy). The `MIC` and `TIC` index curves are convex while others are concave. The stringy curve shows an instantaneous jump to the optimum when aproaching the best basis." 
sq_basis_dist_idx |>
  ggplot(aes(x = dist, y = index, group = index_name)) +
  geom_point() +
  facet_nested_wrap(~index + n, nrow = 3, labeller = label_both) + 
  xlab("projection distance") + ylab("index value") 
```
